Biden to win the popular vote in the 2020 American presidential elections

### 2020-11-03 outputs/paper/paper.Rmd
Updated plots

```{r map, fig.cap = "Election predictions by state.", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/map.pdf"))
```

>>>>

```{r map, fig.cap = "Trump favorability by state.", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/map.pdf"))
```

```{r state, fig.cap = "Survey versus poststrat by state.", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/survey_versus_poststrat_state.pdf"))
```

```{r age, fig.cap = "Survey versus poststrat by age", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/survey_versus_poststrat_age.pdf"))
```

```{r race, fig.cap = "Predicted Republican vote by race", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/predicted_republican_race.pdf"))
```

```{r educ, fig.cap = "Education post-stratification estimates", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/predicted_republican_education.pdf"))
```

```{r emp, fig.cap = "Employment post-stratification estimates", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/predicted_republican_employment.pdf"))
```

```{r gender, fig.cap = "Gender post-stratification estimates", include = TRUE, echo = FALSE}
knitr::include_graphics(here::here("outputs/figures/predicted_republican_gender.pdf"))
```
